Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-07 discussion.tex
intro to evolution
cleaned up quite nicely section 2

@@

>>>>

- could even start with this: NOTHING PREVENTS GENERALIZATION
In this article we take as an example the Flask case study
and of the \tool as a dashboard. 
But there is nothing that prevents the generalization of 
our approach to other languages and technologies.

@@

- branches. the system does not care. it links to whatever commit is the current one. it could be that visualizations could be developed to comapre branches, but this optiona. future work.

### 2018-04-07 introductory.tex
cleaned up quite nicely section 2

%\todo{Either leave as is or add more info on usage by college if possible}
\subsection{An Ecosystem With a Service API at its Core}
\label{sec:api}
\label{sec:case}

@@

  \Fref{fig:zeeguuarch} presents a high-level view of the case study ecosystem.  The core API is implemented with Flask and Python provides and correspondingly three types of functionality: contextual translations, personalized exercise suggestions, and article recommendations. In total, the API provides a bit under 50 endpoints, out of which around a dozen are very frequently used. The development of the core API itself is a research project. One of the is part of the developer team that maintains and evolves the \zee API.

    \begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\linewidth]{zeeguu-architecture}
      \caption{The architecture of the Zeeguu ecosystem}
      \label{fig:zeeguuarch}
    \end{figure}

  At the time of writing, the ecosystem consists of a reader web application, a web-based exercises platform, and a smartwatch application, which are used by more than \activeUserCount active users on a regular basis. The highest load we observed until now on the API consisted of 12K requests in a single day.

  We will use this \zee API as a case study for this paper. 
  All the figures and measurements in this paper are captured from the actual deployment of \tool in the context of the \zee API. The figures are interactive offering basic data exploration capabilities: filter, zoom, and details on demand\cite{Shne99a}. The \tool deployment for the case study can be accessed publicly\footnote{\url{https://zeeguu.unibe.ch/api/dashboard}; username: {\em guest}, password: {\em soap-sac}}.

@@

The \tool has been deployed with the case study API for 
ten months, time in which more than 112.000 hits of the API have 
been recorded. \va{which ten months?}

The users come from several Dutch highschools and a language center associated with a DutchUniversity. However, some users are using it on their own, outside of any formal educational context. The learners use \zee to study a variety of of foreign languages including German, Dutch, French. They have also diverse native languages, including: Chinese, Dutch, and English.

The highest load we observed until now on the API consisted of 12K requests in a single day. \va{not sure what can be added here; maybe that's enough}

\subsection*{Role of Authors in the Case Study}
\va{not sure what else you would like to add here...}

Another one of the authors is the main developer in a team 
that develops the \tool.

\subsection*{TO ARGUE: NOTHING PREVENTS GENERALIZATION}
\va{Move this to the discussion section - it's premature to discuss this here} 
In this article we take as an example the Flask case study
and of the \tool as a dashboard. 
But there is nothing that prevents the generalization of 
our approach to other languages and technologies.

>>>>

\subsection{An Ecosystem With a Service API at its Core}
\label{sec:api}
\label{sec:case}

@@

  \Fref{fig:zeeguuarch} presents a high-level view of the case study ecosystem.  The core API is implemented with Flask and Python provides and correspondingly three types of functionality: contextual translations, personalized exercise suggestions, and article recommendations. In total, the API provides a bit under 50 endpoints, out of which around a dozen are very frequently used. The development of the core API itself is a research project. One of the authors of this paper is part of the developer team that maintains and evolves the \zee API.

    \begin{figure}[h!]
      \centering
      \includegraphics[width=0.7\linewidth]{zeeguu-architecture}
      \caption{The architecture of the \zee ecosystem}
      \label{fig:zeeguuarch}
    \end{figure}

  At the time of writing, the ecosystem consists of a reader web application, a web-based exercises platform, and a smartwatch application, which are used by more than \activeUserCount active users on a regular basis. The users come from several Dutch highschools and a language center associated with a Dutch University. Several users are using it on their own, outside of any formal educational context. The learners use \zee to study a variety of of foreign languages including German, Dutch, French. They have also diverse native languages, including: Chinese, Dutch, and English. The system can scale to many languages by delegating the machine translation tasks to third party APIs.

  The \tool has been deployed with the case study API for 
  ten months (between June 2017 and the time of writing this
  article, April 2018), time in which more than 112.000 hits 
  of the API have been recorded. The highest load observed 
  until now on the API consisted of 12K requests in a single day.

  All the figures and measurements in this paper are captured from the actual deployment of \tool in the context of the \zee API. The figures are interactive offering basic data exploration capabilities: filter, zoom, and details on demand\cite{Shne99a}. The \tool deployment for the case study can be accessed publicly\footnote{\url{https://zeeguu.unibe.ch/api/dashboard}; username: {\em guest}, password: {\em icsme}}.

  We will use this \zee API as a case study for this paper.

@@
